\chapter{Conclusion \& Future work}
During this graduation project, we touched on many areas in the world of medicine and informatics. Many technologies and tools have been explored through the previous chapters, starting with data integration systems and analytics to visualization. Each technology represents a universe to be discovered and many other areas still remain to be explored in the field of data integration and analyses.
\bigbreak
In this thesis, we introduced medical informatics presenting all the different data types and actors contributing to it. We also presented the information visualization field, the visualization pipeline and we have seen the data warehouse definition, and the various data integration approaches.\\
In our work, we presented a visualization system that deals with multiple data sources and produces a structured data file presented in an XML format that could be easily visualized to the multiple medical actors through their personalized dashboards. To achieve this system, it was essential to ensure having the right tools and good practices for better results. 
In our case, we were limited to open source tools, which in a way limited us.
\bigbreak
This work remains a first version acting as a small proof of concept and example of this idea of a "personalized dashboard for healthcare". Several points could improve this system, we mention:
\begin{itemize}
\renewcommand{\labelitemi}{$\bullet$}
\item Automate the rendering process.
\item Introduce continuous data integration.
\item Combine the processing step with some Machine Learning system.
\item Protect the application and data using some security system.
\item Offer more dynamic outputs depending on user's needs and preferences.
\end{itemize}
